The Mysterious Lives Of Speckles. I. Residual atmospheric speckle lifetimes in ground-based coronagraphs

### 2021-05-25 specklelives.tex
updated

\section{The Potential of \textbf{PSF} Reconstruction Post-Processing}
\label{sec:reconstruction}
\textbf{The reconstruction of the post-AO PSF using AO system telemetry has been studied for some time, primarily focused on the long-exposure PSF, e.g. \citet{1997JOSAA..14.3057V} and see the recent review by \citep{2020SPIE11448E..0AB}.  PSF reconstruction in the context of high-contrast imaging is mainly concerned with short exposures and typically has been based on image data alone \citep{2006ApJ...641..556M,2007ApJ...660..770L,2012ApJ...755L..28S}, however the potential for telemetry-based PSF estimation in high-contrast imaging has been recognized \citep{2013ApJ...767...21F,2013ApJ...767..100C}. Here we use our treatment of the intensity dynamics behind an AO-fed coronagraph to analyze the performance of PSF estimation and subtraction, particularly motivated by the use of WFS telemetry to improve on the sensitivity limit set by atmospheric speckle lifetimes.}

>>>>

\section{The Potential of \textbf{PSF} Reconstruction Post-Processing}
\label{sec:reconstruction}
\textbf{The reconstruction of the post-AO PSF using AO system telemetry has been studied for some time, primarily focused on the long-exposure PSF, e.g. \citet{1997JOSAA..14.3057V} and see the recent review by \citep{2020SPIE11448E..0AB}.  PSF reconstruction in the context of high-contrast imaging is typically based on image data alone \citep{2006ApJ...641..556M,2007ApJ...660..770L,2012ApJ...755L..28S}, however the potential for telemetry-based PSF estimation in high-contrast imaging has been recognized \citep{2013ApJ...767...21F,2013ApJ...767..100C}. Here we use our treatment of the intensity dynamics behind an AO-fed coronagraph to analyze the performance of PSF estimation and subtraction.  We are particularly motivated by the use of WFS telemetry to improve on the sensitivity limit set by atmospheric speckle lifetimes, however this analysis could be applied to conventional post-processing such as the KLIP algorithm \citep{2012ApJ...755L..28S}.}
